---
title: "plot_DGN-calc-weights_20150216"
author: "Heather E. Wheeler"
date: "`r Sys.time()`"
output: html_document
---

###DGN-WB Elastic Net 10-fold CV Results for gene expression prediction (SNPs within 1Mb of each gene)
####Compare alpha=0.5 to alpha=1
```{r,compareEN,fig.width=5,fig.height=5}
library(ggplot2)
library(reshape2)
library(dplyr)
"%&%" = function(a,b) paste(a,b,sep="")
alpha1 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_elasticNet_alpha1_imputedSNPs_chr1-22_2015-02-02.txt', header=T)
alpha0.5 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_elasticNet_alpha0.5_imputedSNPs_chr1-22_2015-02-02.txt', header=T)
dim(alpha1)
dim(alpha0.5)
en <- inner_join(alpha1,alpha0.5,by="gene")
with(en,plot(R2.x,R2.y,xlab='alpha=1 R2',ylab='alpha=0.5 R2',xlim=c(0,1),ylim=c(0,1),main='E-N DGN-WB all 13K protein coding genes',cex=0.5,col=rgb(100,100,100,100,maxColorValue=255)))
abline(0,1,col="red")
with(en,t.test(R2.x>R2.y))
```

####Compare polyscore thresholds
```{r,comparePS}
"%&%" = function(a,b) paste(a,b,sep="")
ps4 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh1e-04_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
ps3 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh0.001_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
ps2 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh0.01_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
ps05 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh0.05_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
ps5 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh0.5_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
ps1 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh1_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
ps4 <- ps4 %>% select(gene,CV.R2)
ps3 <- ps3 %>% select(gene,CV.R2)
ps2 <- ps2 %>% select(gene,CV.R2)
ps05 <- ps05 %>% select(gene,CV.R2)
ps5 <- ps5 %>% select(gene,CV.R2)
ps1 <- ps1 %>% select(gene,CV.R2)
all <- inner_join(ps4,ps3,by='gene')
colnames(all) <- c('gene',0.0001,0.001)
all <- inner_join(all,ps2,by='gene')
colnames(all) <- c('gene',0.0001,0.001,0.01)
all <- inner_join(all,ps05,by='gene')
colnames(all) <- c('gene',0.0001,0.001,0.01,0.05)
all <- inner_join(all,ps5,by='gene')
colnames(all) <- c('gene',0.0001,0.001,0.01,0.05,0.5)
all <- inner_join(all,ps1,by='gene')
colnames(all) <- c('gene',0.0001,0.001,0.01,0.05,0.5,1)
all <- all[complete.cases(all),]
all_long <- melt(all,by=gene)
ngenes<-dim(all)[1]
p <- ggplot(all_long, aes(x = -log10(as.numeric(levels(variable))[variable]), y = value), group=gene) + geom_line(lwd = 0.5, show_guide = FALSE) + aes(color = gene) + xlab("-log10(p) threshold") + ylab("R2") + ggtitle("Polyscore DGN-WB (" %&% ngenes %&% " protein coding genes)")
print(p)

p <- ggplot(all_long, aes(x = -log10(as.numeric(levels(variable))[variable]), y = value), group=gene) + geom_line(lwd = 0.5, show_guide = FALSE) + aes(color = gene) + xlab("-log10(p) threshold") + ylab("R2") + ggtitle("Polyscore DGN-WB (protein coding genes with R2>0.5)") + coord_cartesian(ylim=c(0.5,0.9))
print(p)
```

####Compare polyscore to E-N
```{r,comparePS-EN,fig.width=5,fig.height=5}
"%&%" = function(a,b) paste(a,b,sep="")
alpha1 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_elasticNet_alpha1_imputedSNPs_chr1-22_2015-02-02.txt', header=T)
ps4 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh1e-04_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
ps05 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh0.05_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
all <- inner_join(alpha1,ps4,by='gene')
all <- inner_join(all,ps05,by='gene')
with(all,plot(R2,CV.R2.x,xlab='LASSO (alpha=1) R2',ylab='Polyscore P < 0.0001 R2',xlim=c(0,1),ylim=c(0,1),main='DGN-WB predictive performance',cex=0.5,col=rgb(100,100,100,100,maxColorValue=255)))
abline(0,1,col="red")
with(all,t.test(R2>CV.R2.x))
with(all,plot(R2,CV.R2.y,xlab='LASSO (alpha=1) R2',ylab='Polyscore P < 0.05 R2',xlim=c(0,1),ylim=c(0,1),main='DGN-WB predictive performance',cex=0.5,col=rgb(100,100,100,100,maxColorValue=255)))
abline(0,1,col="red")
with(all,t.test(R2>CV.R2.y))
with(all,plot(CV.R2.x,CV.R2.y,xlab='Polyscore P < 0.0001 R2',ylab='Polyscore P < 0.05 R2',xlim=c(0,1),ylim=c(0,1),main='DGN-WB predictive performance',cex=0.5,col=rgb(100,100,100,100,maxColorValue=255)))
abline(0,1,col="red")
with(all,t.test(CV.R2.x>CV.R2.y))

ps2 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh0.01_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
all <- inner_join(all,ps2,by='gene')
with(all,plot(CV.R2.x,CV.R2,xlab='Polyscore P < 0.0001 R2',ylab='Polyscore P < 0.01 R2',xlim=c(0,1),ylim=c(0,1),main='DGN-WB predictive performance',cex=0.5,col=rgb(100,100,100,100,maxColorValue=255)))
abline(0,1,col="red")
with(all,t.test(CV.R2.x>CV.R2))
```

####Compare n.snps per model
```{r,nsnps,fig.width=5,fig.height=5}
alpha1 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_elasticNet_alpha1_imputedSNPs_chr1-22_2015-02-02.txt', header=T)
alpha0.5 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_elasticNet_alpha0.5_imputedSNPs_chr1-22_2015-02-02.txt', header=T)
ps4 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh1e-04_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
ps05 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh0.05_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
alpha1 <- alpha1 %>% select(gene,n.snps)
alpha0.5 <- alpha0.5 %>% select(gene,n.snps)
ps4 <- ps4 %>% select(gene,n.snps)
ps05 <- ps05 %>% select(gene,n.snps)
all <- inner_join(alpha1,alpha0.5,by='gene')
all <- inner_join(all,ps4,by='gene')
all <- inner_join(all,ps05,by='gene')
colnames(all) <- c('gene','EN.a=1','EN.a=0.5','PS.e-04','PS.0.05')
all_long <- melt(all,by=gene)
p <- ggplot(all_long, aes(x = variable, y = value))
p + geom_boxplot() + ggtitle("Number of SNPs in predictive model") + xlab("model") + ylab("n SNPs")
p <- ggplot(all_long, aes(x = variable, y = value))
p + geom_boxplot() + ggtitle("Number of SNPs in predictive model") + xlab("model") + ylab("n SNPs") + coord_cartesian(ylim=c(0,250))
```

####Compare LASSO R2 to gcta local h2
```{r,lassovh2}
"%&%" = function(a,b) paste(a,b,sep="")
alpha1 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_elasticNet_alpha1_imputedSNPs_chr1-22_2015-02-02.txt', header=T)
h2 <- read.table('/Users/heather/Dropbox/cis.v.trans.prediction/DGN-WB.localGRM.h2.exp.2014-08-30.txt',header=T)
all <- inner_join(alpha1,h2,by='gene')
data <- all %>% mutate(ymin = pmax(0, h2 - 2 * se), ymax = pmin(1, h2 + 2 * se) ) %>% arrange(h2)
data <- data[complete.cases(data),]
p1<-ggplot(data,aes(x=1:nrow(data),y=h2,ymin=ymin, ymax=ymax) ) + geom_pointrange(col='gray')+geom_point()
p1 + geom_point(data=data,aes(x=1:nrow(data),y=R2),color='red',cex=0.5) + xlab("Genes sorted by h2") + ylab("h2 (black) or R2 (red)") + ggtitle('DGN-WB Local h2 (black) and LASSO 10-fold CV R2 (red)')
##calc %genes with R2 that reaches lower bound of h2 estimate
count<-data$R2>data$ymin
table(count)
sum(table(count))
table(count)/sum(table(count))
```

####Compare polyscore R2 to gcta local h2
```{r,PSvh2}
"%&%" = function(a,b) paste(a,b,sep="")
ps4 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh1e-04_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
h2 <- read.table('/Users/heather/Dropbox/cis.v.trans.prediction/DGN-WB.localGRM.h2.exp.2014-08-30.txt',header=T)
all <- inner_join(ps4,h2,by='gene')
data <- all %>% mutate(ymin = pmax(0, h2 - 2 * se), ymax = pmin(1, h2 + 2 * se) ) %>% arrange(h2)
data <- data[complete.cases(data),]
p1<-ggplot(data,aes(x=1:nrow(data),y=h2,ymin=ymin, ymax=ymax) ) + geom_pointrange(col='gray')+geom_point()
p1 + geom_point(data=data,aes(x=1:nrow(data),y=CV.R2),color='red',cex=0.5) + xlab("Genes sorted by h2") + ylab("h2 (black) or R2 (red)") + ggtitle('DGN-WB Local h2 (black) and Polyscore (P<e-04) 10-fold CV R2 (red)')
##calc %genes with R2 that reaches lower bound of h2 estimate
count<-data$CV.R2>data$ymin
table(count)
sum(table(count))
table(count)/sum(table(count))
##calc prop genes with h2>0.1
a<-h2$h2>0.1
table(a)/sum(table(a))
##calc prop genes with h2>0.01
a<-h2$h2>0.01
table(a)/sum(table(a))
```

####Compare gcta local h2 to mean expression level
```{r,localh2vexp}
h2 <- read.table('/Users/heather/Dropbox/cis.v.trans.prediction/DGN-WB.localGRM.h2.exp.2014-08-30.txt',header=T)
exp <- read.table('/Users/heather/Dropbox/cis.v.trans.prediction/DGN-WB.mean.median.expression.2015-02-23.txt',header=T)
all <- inner_join(h2,exp,by='gene')
dim(all)
ggplot(all,aes(x=h2,y=expmeans)) + geom_point() + geom_smooth(method = "lm") + xlab("Local h2") + ylab("Mean expression") + ggtitle("DGN-WB (each point is a gene)")
summary(lm(expmeans~h2,all))
##No relationship between mean expression and h2
ggplot(all,aes(x=h2,y=expmedians)) + geom_point() + geom_smooth(method = "lm") + xlab("Local h2") + ylab("Median expression") + ggtitle("DGN-WB (each point is a gene)")
summary(lm(expmedians~h2,all))
##Lower median expression has a larger h2
toph2 <- all[all[,2]>0.1,]
dim(toph2)
ggplot(toph2,aes(x=h2,y=expmedians)) + geom_point() + geom_smooth(method = "lm") + xlab("Local h2") + ylab("Median expression") + ggtitle("DGN-WB h2>0.1 (each point is a gene)")
summary(lm(expmedians~h2,toph2))
##Lower median expression has a larger h2
```

####Compare polyscore thresholds
```{r,compareAllCV}
"%&%" = function(a,b) paste(a,b,sep="")
library(GGally)
alpha1 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_elasticNet_alpha1_imputedSNPs_chr1-22_2015-02-02.txt', header=T)
alpha0.5 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_elasticNet_alpha0.5_imputedSNPs_chr1-22_2015-02-02.txt', header=T)
ps4 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh1e-04_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
ps3 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh0.001_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
ps2 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh0.01_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
ps05 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh0.05_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
ps5 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh0.5_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
ps1 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh1_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
alpha1 <- alpha1 %>% select(gene,R2)
alpha0.5<-alpha0.5 %>% select(gene,R2)
ps4 <- ps4 %>% select(gene,CV.R2)
ps3 <- ps3 %>% select(gene,CV.R2)
ps2 <- ps2 %>% select(gene,CV.R2)
ps05 <- ps05 %>% select(gene,CV.R2)
ps5 <- ps5 %>% select(gene,CV.R2)
ps1 <- ps1 %>% select(gene,CV.R2)
all <- inner_join(alpha1,alpha0.5,by='gene')
colnames(all) <- c('gene','lasso','eNet')
all <- inner_join(all,ps4,by='gene')
colnames(all) <- c('gene','lasso','eNet','poly0.0001')
all <- inner_join(all,ps3,by='gene')
colnames(all) <- c('gene','lasso','eNet','poly0.0001','poly0.001')
all <- inner_join(all,ps2,by='gene')
colnames(all) <- c('gene','lasso','eNet','poly0.0001','poly0.001','poly0.01')
all <- inner_join(all,ps05,by='gene')
colnames(all) <- c('gene','lasso','eNet','poly0.0001','poly0.001','poly0.01','poly0.05')
all <- inner_join(all,ps5,by='gene')
colnames(all) <- c('gene','lasso','eNet','poly0.0001','poly0.001','poly0.01','poly0.05','poly0.5')
all <- inner_join(all,ps1,by='gene')
colnames(all) <- c('gene','lasso','eNet','poly0.0001','poly0.001','poly0.01','poly0.05','poly0.5','poly1')
all <- all[complete.cases(all),]
p<-ggpairs(all[,2:9],lower=list(continuous="points",params=c(cex=0.5,ylim=c(0,1),xlim=c(0,1))),diag=list(continuous='blank'),title="Predictive Performance (R2 of GReX vs. observed expression)")
tiff(filename="ggpairs_DGN-WB_10-fCV.tiff",width=960,height=960)
print(p)
dev.off()
png(filename="ggpairs_DGN-WB_10-fCV.png",width=960,height=960)
print(p)
dev.off()
print(p)
```


####Compare LASSO and Polyscore R2 to gcta local h2
```{r,lassoAndPSvh2}
"%&%" = function(a,b) paste(a,b,sep="")
alpha1 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_elasticNet_alpha1_imputedSNPs_chr1-22_2015-02-02.txt', header=T)
h2 <- read.table('/Users/heather/Dropbox/cis.v.trans.prediction/DGN-WB.localGRM.h2.exp.2014-08-30.txt',header=T)
ps4 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh1e-04_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
all <- inner_join(alpha1,h2,by='gene')
all <- inner_join(all,ps4,by='gene')
data <- all %>% mutate(ymin = pmax(0, h2 - 2 * se), ymax = pmin(1, h2 + 2 * se) ) %>% arrange(h2)
data <- data[complete.cases(data),]
p1<-ggplot(data,aes(x=1:nrow(data),y=h2,ymin=ymin, ymax=ymax) ) + geom_pointrange(col='gray')+geom_point()
p1<-p1 + geom_point(data=data,aes(x=1:nrow(data),y=R2),color='red',cex=0.5) + xlab("Genes sorted by h2") + ylab("h2 (black) or R2 (red)") + ggtitle('LASSO predictive performance (R2) compared to local heritability (h2)')
p2<-ggplot(data,aes(x=1:nrow(data),y=h2,ymin=ymin, ymax=ymax) ) + geom_pointrange(col='gray')+geom_point()
p2<-p2 + geom_point(data=data,aes(x=1:nrow(data),y=CV.R2),color='red',cex=0.5) + xlab("Genes sorted by h2") + ylab("h2 (black) or R2 (red)") + ggtitle('Polygenic score (P<1e-04) predictive performance (R2) compared to local heritability (h2)')
library(grid)
pushViewport(viewport(layout = grid.layout(2, 1)))
print(p1, vp = viewport(layout.pos.row = 1, layout.pos.col = 1))
print(p2, vp = viewport(layout.pos.row = 2, layout.pos.col = 1))
```

####Compare LASSO and Polyscore R2 to gcta local h2
```{r,lassoAndPSvh2take2}
"%&%" = function(a,b) paste(a,b,sep="")
alpha1 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_elasticNet_alpha1_imputedSNPs_chr1-22_2015-02-02.txt', header=T)
h2 <- read.table('/Users/heather/Dropbox/cis.v.trans.prediction/DGN-WB.localGRM.h2.exp.2014-08-30.txt',header=T)
ps4 <- read.table('/Users/heather/Dropbox/elasticNet_testing/DGN-imputed-CV_20150209/DGN-WB_exp_10-foldCV_polyscore_Pthresh1e-04_imputedSNPs_chr1-22_2015-02-09.txt',header=T)
alpha1h2 <- inner_join(alpha1,h2,by='gene')
dataL <- alpha1h2 %>% mutate(ymin = pmax(0, h2 - 2 * se), ymax = pmin(1, h2 + 2 * se)) %>% arrange(h2) %>% select(gene,R2,h2,ymin,ymax)
dataL <- dataL %>% mutate(method="LASSO",position=1:nrow(dataL))
ps4h2 <- inner_join(ps4,h2,by='gene')
dataP <- ps4h2 %>% mutate(ymin = pmax(0, h2 - 2 * se), ymax = pmin(1, h2 + 2 * se)) %>% arrange(h2) %>% select(gene,CV.R2,h2,ymin,ymax)
dataP <- dataP %>% mutate(method="Polyscore",position=1:nrow(dataP))
colnames(dataP) <- c('gene','R2','h2','ymin','ymax','method','position')
data<-rbind(dataL,dataP)
data <- data[complete.cases(data),]
p1<-ggplot(data,aes(x=position,y=h2,ymin=ymin, ymax=ymax) ) + geom_pointrange(col='gray')+geom_point()+facet_wrap(~method,ncol=1)
p1<- p1 + geom_point(data=data,aes(x=position,y=R2),color='red',cex=0.8) + xlab("Genes sorted by h2") + ylab("h2 (black) or R2 (red)") +theme_bw(40)
png(filename="compareR2_h2.png",width=720,height=960)
print(p1)
dev.off()
tiff(filename="compareR2_h2.tiff",width=360,height=480)
print(p1)
dev.off()
p1
```