---
title: "GTEx_multitissue_comparison"
author: "Heather E. Wheeler"
date: "`r Sys.time()`"
output: html_document
---

Stephens lab data accessed from <http://www.gtexportal.org/static/datasets/gtex_analysis_pilot_v3/multi_tissue_eqtls/Multi_tissue_eQTL_GTEx_Pilot_Phase_datasets.tar> on 20150722.

From README: "We are using the eQTL posterior probabilities from the UC Multi-tissue eQTL method (doi:10.1371/journal.pgen.1003486) for each of the 9 tissues analyzed in the pilot phase (Adipose_subcutaneous, Artery_Tibal, Whole_Blood, Heart_Left_Ventricle, Lung, Muscle_Skeletal, Nerve_Tibial, Skin_Lower_Leg_Sun_Exposed, Thyroid) in the file `res_final_uc_com_genes_com_snps.txt.gz`. These values may be interpreted as Pr(SNP is eQTL in tissue s | data). 9875 eGenes are presented, with the "top" (most significant) SNP in each gene used."

```{r, getData, message=FALSE}
library(plyr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(GGally)
"%&%" = function(a,b) paste(a,b,sep="")
mt.dir <- "~/GitHub/GenArch/GenArchPaper/UC_Stephens_Multitissue_Comp/"
#tarbell mt.dir <- "/Volumes/im-lab/nas40t2/hwheeler/cross-tissue/Multi_tissue_eQTL_GTEx_Pilot_Phase_datasets/"
h2.dir <- "~/GitHub/GenArch/GenArchPaper/BSLMM/bslmm_gtex_results/"
#tarbell h2.dir <- "/Volumes/im-lab/nas40t2/hwheeler/cross-tissue/"
bslmm.dir <- "~/GitHub/GenArch/GenArchPaper/BSLMM/bslmm_gtex_results/"
#tarbell bslmm.dir <- "/Volumes/im-lab/nas40t2/hwheeler/cross-tissue/BSLMM_exp/"
mt <- read.table(mt.dir %&% "res_final_uc_com_genes_com_snps.txt.gz",header=TRUE)
head(mt)
dim(mt)
#remove version number in order to compare ensembl IDs
a <- substr(mt$gene,1,15)
mt <- mutate(mt,gene=a)
h2.ts <- read.table(bslmm.dir %&% "GTEx_Tissue-Specific_local_h2.txt",header=TRUE)
#remove version number in order to compare ensembl IDs
a <- substr(h2.ts$ensid,1,15)
h2.ts <- mutate(h2.ts,gene=a)
h2.tw <- read.table(bslmm.dir %&% "GTEx_Tissue-Wide_local_h2.txt",header=TRUE)
#remove version number in order to compare ensembl IDs
a <- substr(h2.tw$ensid,1,15)
h2.tw <- mutate(h2.tw,gene=a)
##Get BSLMM results
pve.ts <- read.table(bslmm.dir %&% "GTEx_Tissue-Specific_local_PVE_by_BSLMM.txt",header=TRUE)
#remove version number in order to compare ensembl IDs
pve.ts <- mutate(pve.ts,gene=substr(pve.ts$gene,1,15))
pve.tw <- read.table(bslmm.dir %&% "GTEx_Tissue-Wide_local_PVE_by_BSLMM.txt",header=TRUE)
#remove version number in order to compare ensembl IDs
pve.tw <- mutate(pve.tw,gene=substr(pve.tw$gene,1,15))
```

##Calculate entropy of Pr and correlate with **cross-tissue and tissue-specific** h2 
- higher entropy means more likely to be multi-tissue eQTL (expect positive cor. for entropy vs. cross-tissue h2)
```{r,entropTSh2}
entropy <- function(pr){
  pi <- pr/sum(pr)
  pi[pi==0] <- 1e-06 ##allows log transformation
  -1*sum(pi*log(pi))
}

mtPr <- mt[,3:11]
mtS <- apply(mtPr,1,entropy) ##calc entropy for each row
hist(mtS)
summary(mtS)
geneS <- select(mt,gene) %>% mutate(entropy=mtS) ##put gene and entropy together

tislist <- c('CrossTissue','AdiposeSubcutaneous','ArteryTibial','HeartLeftVentricle','Lung','MuscleSkeletal','NerveTibial','SkinSunExposedLowerleg','Thyroid','WholeBlood')
for(tis in tislist){
  h2.tis <- h2.ts %>% select(gene,one_of(tis)) ##one_of allows character vector
  newdata <- inner_join(geneS,h2.tis,by='gene')
  colnames(newdata)[3] <- "h2"
  p <- ggplot(newdata,aes(x=h2,y=entropy))+geom_point(alpha=0.4)+stat_smooth()+xlab(tis %&% " h2")
  cors <- data.frame(cor=signif(cor(newdata$h2, newdata$entropy), 2))
  p1 <- p + geom_text(data=cors, aes(label=paste("R = ", cor, sep="")), x=-Inf, y=Inf, hjust=-0.2, vjust=1.2, size=4)
  pvals <- data.frame(cor=signif(cor.test(newdata$h2, newdata$entropy)$p.value, 2))
  p2 <- p1 + geom_text(data=pvals, aes(label=paste("p = ", cor, sep="")), x=Inf, y=Inf, hjust=1.2, vjust=1.2, size=4)
  print(p2)
}
```

##Compare entropy of Pr to **tissue-wide** h2 
```{r,entropyTWh2,warning=FALSE}
tislist <- c('AdiposeSubcutaneous','ArteryTibial','HeartLeftVentricle','Lung','MuscleSkeletal','NerveTibial','SkinSunExposedLowerleg','Thyroid','WholeBlood')
for(tis in tislist){
  h2.tis <- h2.tw %>% select(gene,one_of(tis)) ##one_of allows character vector
  newdata <- inner_join(geneS,h2.tis,by='gene')
  colnames(newdata)[3] <- "h2"
  p <- ggplot(newdata,aes(x=h2,y=entropy))+geom_point(alpha=0.4)+stat_smooth()+
    xlab(tis %&% " tissue-wide h2")
  cors <- data.frame(cor=signif(cor(newdata$h2, newdata$entropy), 2))
  p1 <- p + geom_text(data=cors, aes(label=paste("R = ", cor, sep="")), x=-Inf, y=Inf, hjust=-0.2, vjust=1.2, size=4)
  pvals <- data.frame(cor=signif(cor.test(newdata$h2, newdata$entropy)$p.value, 2))
  p2 <- p1 + geom_text(data=pvals, aes(label=paste("p = ", cor, sep="")), x=Inf, y=Inf, hjust=1.2, vjust=1.2, size=4)
  print(p2)
}
```

##Compare entropy of Pr with **cross-tissue and tissue-specific** PVE by BSLMM
```{r,entropyTSpve,warning=FALSE}
tislist <- c('CrossTissue','AdiposeSubcutaneous','ArteryTibial','HeartLeftVentricle','Lung','MuscleSkeletal','NerveTibial','SkinSunExposedLowerleg','Thyroid','WholeBlood')
for(tis in tislist){
  pve.tis <- pve.ts %>% select(gene,one_of(tis)) ##one_of allows character vector
  newdata <- inner_join(geneS,pve.tis,by='gene')
  colnames(newdata)[3] <- "pve"
  p <- ggplot(newdata,aes(x=pve,y=entropy))+geom_point(alpha=0.4)+stat_smooth()+
    xlab(tis %&% " PVE")
  cors <- data.frame(cor=signif(cor(newdata$pve, newdata$entropy, use="p"), 2))
  p1 <- p + geom_text(data=cors, aes(label=paste("R = ", cor, sep="")), x=-Inf, y=Inf, hjust=-0.2, vjust=1.2, size=4)
  pvals <- data.frame(cor=signif(cor.test(newdata$pve, newdata$entropy)$p.value, 2))
  p2 <- p1 + geom_text(data=pvals, aes(label=paste("p = ", cor, sep="")), x=Inf, y=Inf, hjust=1.2, vjust=1.2, size=4)
  print(p2)
}
```

##Compare entropy of Pr with **tissue-wide** PVE by BSLMM
```{r,entropyTWpve,warning=FALSE}
tislist <- c('AdiposeSubcutaneous','ArteryTibial','HeartLeftVentricle','Lung','MuscleSkeletal','NerveTibial','SkinSunExposedLowerleg','Thyroid','WholeBlood')
for(tis in tislist){
  pve.tis <- pve.tw %>% select(gene,one_of(tis)) ##one_of allows character vector
  newdata <- inner_join(geneS,pve.tis,by='gene')
  colnames(newdata)[3] <- "pve"
  p <- ggplot(newdata,aes(x=pve,y=entropy))+geom_point(alpha=0.4)+stat_smooth()+
    xlab(tis %&% " tissue-wide PVE")
  cors <- data.frame(cor=signif(cor(newdata$pve, newdata$entropy, use="p"), 2))
  p1 <- p + geom_text(data=cors, aes(label=paste("R = ", cor, sep="")), x=-Inf, y=Inf, hjust=-0.2, vjust=1.2, size=4)
  pvals <- data.frame(cor=signif(cor.test(newdata$pve, newdata$entropy)$p.value, 2))
  p2 <- p1 + geom_text(data=pvals, aes(label=paste("p = ", cor, sep="")), x=Inf, y=Inf, hjust=1.2, vjust=1.2, size=4)
  print(p2)
}
```

#Compare Pr(SNP is eQTL in tissue s | data) to local h2 for each gene
##Tissue-Specific h2 (from OTD)

```{r, ts, message=FALSE,warning=FALSE}
data <- inner_join(mt,h2.ts,by='gene')
dim(data)
##only half overlap, why? gcta didn't converge? multi-tissue model didn't converge?

#test one tissue h2 at a time
tislist <- c('AdiposeSubcutaneous','ArteryTibial','HeartLeftVentricle','Lung','MuscleSkeletal','NerveTibial','SkinSunExposedLowerleg','Thyroid','WholeBlood')

for(tis in tislist){
  h2.tis <- h2.ts %>% select(gene,one_of(tis)) ##one_of allows character vector
  newdata <- inner_join(mt,h2.tis,by='gene')
  gdata <- gather(newdata,"tissue","Pr",3:11)
  colnames(gdata)[3] <- "h2"
  p <- ggplot(gdata,aes(x=h2,y=Pr))+facet_wrap(~tissue)+geom_point(alpha=0.4)+stat_smooth()+
    coord_cartesian(ylim=c(-0.05,1.2))+xlab(tis %&% " h2")
  cors <- ddply(gdata, .(tissue), summarise, cor = signif(cor(h2, Pr), 2))
  p1 <- p + geom_text(data=cors, aes(label=paste("R = ", cor, sep="")), x=-Inf, y=Inf, hjust=-0.2, vjust=1.2, size=3)
  pvals <- ddply(gdata, .(tissue), summarise, cor = signif(cor.test(h2, Pr)$p.value, 2))
  p2 <- p1 + geom_text(data=pvals, aes(label=paste("p = ", cor, sep="")), x=Inf, y=Inf, hjust=1.2, vjust=1.2, size=3)
  print(p2)
}
```

##Cross-Tissue h2 (from OTD)
```{r, ct, message=FALSE,warning=FALSE}
tis <- 'CrossTissue'
h2.tis <- h2.ts %>% select(gene,one_of(tis)) ##one_of allows character vector
newdata <- inner_join(mt,h2.tis,by='gene')
gdata <- gather(newdata,"tissue","Pr",3:11)
colnames(gdata)[3] <- "h2"
p <- ggplot(gdata,aes(x=h2,y=Pr))+facet_wrap(~tissue)+geom_point(alpha=0.4)+stat_smooth()+
  coord_cartesian(ylim=c(-0.05,1.2))+xlab(tis %&% " h2")
cors <- ddply(gdata, .(tissue), summarise, cor = signif(cor(h2, Pr), 2))
p1 <- p + geom_text(data=cors, aes(label=paste("R = ", cor, sep="")), x=-Inf, y=Inf, hjust=-0.2, vjust=1.2, size=3)
pvals <- ddply(gdata, .(tissue), summarise, cor = signif(cor.test(h2, Pr)$p.value, 2))
p2 <- p1 + geom_text(data=pvals, aes(label=paste("p = ", cor, sep="")), x=Inf, y=Inf, hjust=1.2, vjust=1.2, size=3)
print(p2)
```

##Tissue-Wide h2
```{r, tw, message=FALSE,warning=FALSE}
#test one tissue h2 at a time
tislist <- c('AdiposeSubcutaneous','ArteryTibial','HeartLeftVentricle','Lung','MuscleSkeletal','NerveTibial','SkinSunExposedLowerleg','Thyroid','WholeBlood')
for(tis in tislist){
  h2.tis <- h2.tw %>% select(gene,one_of(tis)) ##one_of allows character vector
  newdata <- inner_join(mt,h2.tis,by='gene')
  gdata <- gather(newdata,"tissue","Pr",3:11)
  colnames(gdata)[3] <- "h2"
  p <- ggplot(gdata,aes(x=h2,y=Pr))+facet_wrap(~tissue)+geom_point(alpha=0.4)+stat_smooth()+
    coord_cartesian(ylim=c(-0.05,1.2))+xlab(tis %&% " tissue-wide h2")
  cors <- ddply(gdata, .(tissue), summarise, cor = signif(cor(h2, Pr), 2))
  p1 <- p + geom_text(data=cors, aes(label=paste("R = ", cor, sep="")), x=-Inf, y=Inf, hjust=-0.2, vjust=1.2, size=3)
  pvals <- ddply(gdata, .(tissue), summarise, cor = signif(cor.test(h2, Pr)$p.value, 2))
  p2 <- p1 + geom_text(data=pvals, aes(label=paste("p = ", cor, sep="")), x=Inf, y=Inf, hjust=1.2, vjust=1.2, size=3)
  print(p2)
}
```

#Compare Pr(SNP is eQTL in tissue s | data) to local PVE by BSLMM for each gene
##Tissue-Specific PVE (from OTD)

```{r, tsPVE, message=FALSE,warning=FALSE}
data <- inner_join(mt,pve.ts,by='gene')
dim(data)
##only half overlap, why? same overlap as with h2? max overlap b/t gencode versions?

#test one tissue pve at a time
tislist <- c('AdiposeSubcutaneous','ArteryTibial','HeartLeftVentricle','Lung','MuscleSkeletal','NerveTibial','SkinSunExposedLowerleg','Thyroid','WholeBlood')

for(tis in tislist){
  pve.tis <- pve.ts %>% select(gene,one_of(tis)) ##one_of allows character vector
  newdata <- inner_join(mt,pve.tis,by='gene')
  gdata <- gather(newdata,"tissue","Pr",3:11)
  colnames(gdata)[3] <- "pve"
  p <- ggplot(gdata,aes(x=pve,y=Pr))+facet_wrap(~tissue)+geom_point(alpha=0.4)+stat_smooth()+
    coord_cartesian(ylim=c(-0.05,1.2))+xlab(tis %&% " PVE")
  cors <- ddply(gdata, .(tissue), summarise, cor = signif(cor(pve, Pr, use='p'), 2))
  p1 <- p + geom_text(data=cors, aes(label=paste("R = ", cor, sep="")), x=-Inf, y=Inf, hjust=-0.2, vjust=1.2, size=3)
  pvals <- ddply(gdata, .(tissue), summarise, cor = signif(cor.test(pve, Pr)$p.value, 2))
  p2 <- p1 + geom_text(data=pvals, aes(label=paste("p = ", cor, sep="")), x=Inf, y=Inf, hjust=1.2, vjust=1.2, size=3)
  print(p2)
}
```

##Cross-Tissue PVE (from OTD)
```{r, ctPVE, message=FALSE,warning=FALSE}
tis <- 'CrossTissue'
pve.tis <- pve.ts %>% select(gene,one_of(tis)) ##one_of allows character vector
newdata <- inner_join(mt,pve.tis,by='gene')
gdata <- gather(newdata,"tissue","Pr",3:11)
colnames(gdata)[3] <- "pve"
p <- ggplot(gdata,aes(x=pve,y=Pr))+facet_wrap(~tissue)+geom_point(alpha=0.4)+stat_smooth()+
  coord_cartesian(ylim=c(-0.05,1.2))+xlab(tis %&% " PVE")
cors <- ddply(gdata, .(tissue), summarise, cor = signif(cor(pve, Pr, use="p"), 2))
p1 <- p + geom_text(data=cors, aes(label=paste("R = ", cor, sep="")), x=-Inf, y=Inf, hjust=-0.2, vjust=1.2, size=3)
pvals <- ddply(gdata, .(tissue), summarise, cor = signif(cor.test(pve, Pr)$p.value, 2))
p2 <- p1 + geom_text(data=pvals, aes(label=paste("p = ", cor, sep="")), x=Inf, y=Inf, hjust=1.2, vjust=1.2, size=3)
print(p2)
```

##Tissue-Wide PVE
```{r, twPVE, message=FALSE,warning=FALSE}
#test one tissue pve at a time
tislist <- c('AdiposeSubcutaneous','ArteryTibial','HeartLeftVentricle','Lung','MuscleSkeletal','NerveTibial','SkinSunExposedLowerleg','Thyroid','WholeBlood')
for(tis in tislist){
  pve.tis <- pve.tw %>% select(gene,one_of(tis)) ##one_of allows character vector
  newdata <- inner_join(mt,pve.tis,by='gene')
  gdata <- gather(newdata,"tissue","Pr",3:11)
  colnames(gdata)[3] <- "pve"
  p <- ggplot(gdata,aes(x=pve,y=Pr))+facet_wrap(~tissue)+geom_point(alpha=0.4)+stat_smooth()+
    coord_cartesian(ylim=c(-0.05,1.2))+xlab(tis %&% " tissue-wide PVE")
  cors <- ddply(gdata, .(tissue), summarise, cor = signif(cor(pve, Pr, use="p"), 2))
  p1 <- p + geom_text(data=cors, aes(label=paste("R = ", cor, sep="")), x=-Inf, y=Inf, hjust=-0.2, vjust=1.2, size=3)
  pvals <- ddply(gdata, .(tissue), summarise, cor = signif(cor.test(pve, Pr)$p.value, 2))
  p2 <- p1 + geom_text(data=pvals, aes(label=paste("p = ", cor, sep="")), x=Inf, y=Inf, hjust=1.2, vjust=1.2, size=3)
  print(p2)
}
```

#Compare local h2 to local PVE by BSLMM for each gene
##Cross-Tissue & Tissue-Specific (from OTD)
```{r, tsh2PVE, message=FALSE,warning=FALSE}
tislist <- c('CrossTissue','AdiposeSubcutaneous','ArteryTibial','HeartLeftVentricle','Lung','MuscleSkeletal','NerveTibial','SkinSunExposedLowerleg','Thyroid','WholeBlood')

for(tis in tislist){
  pve.tis <- pve.ts %>% select(gene,one_of(tis)) ##one_of allows character vector
  h2.tis <- h2.ts %>% select(gene,one_of(tis)) ##one_of allows character vector
  newdata <- inner_join(h2.tis,pve.tis,by='gene')
  colnames(newdata)[2:3] <- c("h2","pve")
  p <- ggplot(newdata,aes(x=h2,y=pve))+geom_point(alpha=0.4)+stat_smooth()+xlab(tis %&% " h2")+ylab(tis %&% " PVE")
  cors <- data.frame(cor=signif(cor(newdata$pve, newdata$h2, use="p"), 2))
  p1 <- p + geom_text(data=cors, aes(label=paste("R = ", cor, sep="")), x=-Inf, y=Inf, hjust=-0.2, vjust=1.1, size=3)
  pvals <- data.frame(cor = signif(cor.test(newdata$pve, newdata$h2)$p.value, 2))
  p2 <- p1 + geom_text(data=pvals, aes(label=paste("p = ", cor, sep="")), x=Inf, y=Inf, hjust=1.1, vjust=1.1, size=3)
  print(p2)
}
```

##Tissue-Wide
```{r, twh2PVE, message=FALSE,warning=FALSE}
tislist <- c('AdiposeSubcutaneous','ArteryTibial','HeartLeftVentricle','Lung','MuscleSkeletal','NerveTibial','SkinSunExposedLowerleg','Thyroid','WholeBlood')

for(tis in tislist){
  pve.tis <- pve.tw %>% select(gene,one_of(tis)) ##one_of allows character vector
  h2.tis <- h2.tw %>% select(gene,one_of(tis)) ##one_of allows character vector
  newdata <- inner_join(h2.tis,pve.tis,by='gene')
  colnames(newdata)[2:3] <- c("h2","pve")
  p <- ggplot(newdata,aes(x=h2,y=pve))+geom_point(alpha=0.4)+stat_smooth()+xlab(tis %&% " tissue-wide h2")+ylab(tis %&% " tissue-wide PVE")
  cors <- data.frame(cor=signif(cor(newdata$pve, newdata$h2, use="p"), 2))
  p1 <- p + geom_text(data=cors, aes(label=paste("R = ", cor, sep="")), x=-Inf, y=Inf, hjust=-0.2, vjust=1.1, size=3)
  pvals <- data.frame(cor = signif(cor.test(newdata$pve, newdata$h2)$p.value, 2))
  p2 <- p1 + geom_text(data=pvals, aes(label=paste("p = ", cor, sep="")), x=Inf, y=Inf, hjust=1.1, vjust=1.1, size=3)
  print(p2)
}
```


##Calculate coefficient of variation of Pr and correlate with **cross-tissue and tissue-specific** h2 
- CV = coefficent of variation = sd/mean
- lower CV means more likely to be multi-tissue eQTL (expect neg. cor. for CV vs. cross-tissue h2)
```{r, cvOTD, message=FALSE, eval=FALSE}
meanmt <- apply(mt[,3:11],1,mean)
sdmt <- apply(mt[,3:11],1,sd)
cv <- sdmt/meanmt
newmt<-mutate(mt,CV=cv)

tislist <- c('CrossTissue','AdiposeSubcutaneous','ArteryTibial','HeartLeftVentricle','Lung','MuscleSkeletal','NerveTibial','SkinSunExposedLowerleg','Thyroid','WholeBlood')
for(tis in tislist){
  h2.tis <- h2.ts %>% select(gene,one_of(tis)) ##one_of allows character vector
  newdata <- inner_join(newmt,h2.tis,by='gene')
  colnames(newdata)[13] <- "h2"
  p <- ggplot(newdata,aes(x=h2,y=CV))+geom_point(alpha=0.4)+stat_smooth()+
    xlab(tis %&% " h2")+ylab("Coef of variation (sd/mean) of Pr")
  cors <- data.frame(cor=signif(cor(newdata$h2, newdata$CV), 2))
  p1 <- p + geom_text(data=cors, aes(label=paste("R = ", cor, sep="")), x=-Inf, y=Inf, hjust=-0.2, vjust=1.2, size=4)
  pvals <- data.frame(cor=signif(cor.test(newdata$h2, newdata$CV)$p.value, 2))
  p2 <- p1 + geom_text(data=pvals, aes(label=paste("p = ", cor, sep="")), x=Inf, y=Inf, hjust=1.2, vjust=1.2, size=4)
  print(p2)
}
```

##Compare coefficient of variation of Pr to **tissue-wide** h2 
```{r, cvTW, message=FALSE,eval=FALSE}
meanmt <- apply(mt[,3:11],1,mean)
sdmt <- apply(mt[,3:11],1,sd)
cv <- sdmt/meanmt
newmt<-mutate(mt,CV=cv)

tislist <- c('AdiposeSubcutaneous','ArteryTibial','HeartLeftVentricle','Lung','MuscleSkeletal','NerveTibial','SkinSunExposedLowerleg','Thyroid','WholeBlood')
for(tis in tislist){
  h2.tis <- h2.tw %>% select(gene,one_of(tis)) ##one_of allows character vector
  newdata <- inner_join(newmt,h2.tis,by='gene')
  colnames(newdata)[13] <- "h2"
  p <- ggplot(newdata,aes(x=h2,y=CV))+geom_point(alpha=0.4)+stat_smooth()+
    xlab(tis %&% " tissue-wide h2")+ylab("Coef of variation (sd/mean) of Pr")
  cors <- data.frame(cor=signif(cor(newdata$h2, newdata$CV), 2))
  p1 <- p + geom_text(data=cors, aes(label=paste("R = ", cor, sep="")), x=-Inf, y=Inf, hjust=-0.2, vjust=1.2, size=4)
  pvals <- data.frame(cor=signif(cor.test(newdata$h2, newdata$CV)$p.value, 2))
  p2 <- p1 + geom_text(data=pvals, aes(label=paste("p = ", cor, sep="")), x=Inf, y=Inf, hjust=1.2, vjust=1.2, size=4)
  print(p2)
}
```
