---
title: "100 permutations of h^2^ estimation"
author: "Heather E. Wheeler"
date: "January 13, 2014"
output: html_document
---
I performed 100 resampling permutations for heritability estimation, shuffling the gene expression labels for the DGN-WB and GTEx cross-tissue and orthogonal tissue-specific expression from the linear mixed-model (see cross-tissue_results_2014-11-25.md). Plotted in <span style="color:gray">gray</span> is the sorted h<sup>2</sup> from each permutation and in <span style="color:red">red</span> is the sorted h<sup>2</sup> from the observed data.

```{r,message=FALSE,warning=FALSE}
date <- Sys.Date()
library(dplyr)
library(ggplot2)
library(reshape2)
library(tidyr)
se <- function(x) sqrt(var(x,na.rm=T)/sum(!is.na(x)))
med <- function(x) median(x,na.rm=T)
lci<-function(x) quantile(x, c(.025, 0.975),na.rm=T)[1]
uci<-function(x) quantile(x, c(.025, 0.975),na.rm=T)[2]
sortf<-function(x) sort(x,na.last=FALSE) #sort and add NA's to top
"%&%" = function(a,b) paste(a,b,sep="")
mydir <- "/Users/heather/Dropbox/cross-tissue/"
tissues <- scan('tissue.list.prefix','character',sep='\t')
```
###plot all genes
```{r,message=FALSE,warning=FALSE}
for(i in 1:length(tissues)){
  tis <- tissues[i]
  ##local only
  loconly <- read.table(mydir %&% tis %&% '_h2_localonly_allgenes_100perms_2014-12-19.txt',sep='\t')

  data <- as.matrix(loconly[,5:105]) ##includes observed in first col
  data<-apply(data,2,sortf) ##sort each column
  data[is.na(data)] <- 0 ##replace NA's with 0
  permatrix <- data[,2:ncol(data)] ##pull out the perms
  permL <- melt(permatrix,id=x) ##convert to stacked data for ggplot
  p1 <- ggplot(permL, aes(x=Var1,y=value,group=Var2))
  p1 <- p1 + geom_line(color='gray')
  obs <- as.matrix(data[,1]) ##pull out the observed data to plot thicker
  obsL <- melt(obs,id=x) ##convert to stacked data for ggplot
  losub <- p1 + geom_point(data=obsL,aes(x=Var1,y=value),color='red') + xlab("Genes sorted by h2") + ylab("h2") + ylim(0,1) + ggtitle(tis %&% ' Local (Only) Heritability')
  print(losub)
  
  ##global only
  gloonly <- read.table(tis %&% '_h2_globalonly_allgenes_100perms_2014-12-19.txt',sep='\t')
 
  data <- as.matrix(gloonly[,5:105]) ##includes observed in first col
  data<-apply(data,2,sortf) ##sort each column
  data[is.na(data)] <- 0 ##replace NA's with 0
  permatrix <- data[,2:ncol(data)] ##pull out the perms
  permL <- melt(permatrix,id=x) ##convert to stacked data for ggplot
  p1 <- ggplot(permL, aes(x=Var1,y=value,group=Var2))
  p1 <- p1 + geom_line(color='gray')
  obs <- as.matrix(data[,1]) ##pull out the observed data to plot thicker
  obsL <- melt(obs,id=x) ##convert to stacked data for ggplot
  gosub <- p1 + geom_point(data=obsL,aes(x=Var1,y=value),color='red') + xlab("Genes sorted by h2") + ylab("h2") + ylim(0,1) + ggtitle(tis %&% ' Global (Only) Heritability')
  print(gosub)
  
  ##local joint
  locjoint <- read.table(tis %&% '_h2_localjoint_allgenes_100perms_2014-12-19.txt',sep='\t')
  
  data <- as.matrix(locjoint[,5:105]) ##includes observed in first col
  data<-apply(data,2,sortf) ##sort each column
  data[is.na(data)] <- 0 ##replace NA's with 0
  permatrix <- data[,2:ncol(data)] ##pull out the perms
  permL <- melt(permatrix,id=x) ##convert to stacked data for ggplot
  p1 <- ggplot(permL, aes(x=Var1,y=value,group=Var2))
  p1 <- p1 + geom_line(color='gray')
  obs <- as.matrix(data[,1]) ##pull out the observed data to plot thicker
  obsL <- melt(obs,id=x) ##convert to stacked data for ggplot
  ljsub <- p1 + geom_point(data=obsL,aes(x=Var1,y=value),color='red') + xlab("Genes sorted by h2") + ylab("h2") + ylim(0,1) + ggtitle(tis %&% ' Local (Joint) Heritability')
  print(ljsub)
  
  ##global joint
  glojoint <- read.table(tis %&% '_h2_globaljoint_allgenes_100perms_2014-12-19.txt',sep='\t')
  
  data <- as.matrix(glojoint[,5:105]) ##includes observed in first col
  data<-apply(data,2,sortf) ##sort each column
  data[is.na(data)] <- 0 ##replace NA's with 0
  permatrix <- data[,2:ncol(data)] ##pull out the perms
  permL <- melt(permatrix,id=x) ##convert to stacked data for ggplot
  p1 <- ggplot(permL, aes(x=Var1,y=value,group=Var2))
  p1 <- p1 + geom_line(color='gray')
  obs <- as.matrix(data[,1]) ##pull out the observed data to plot thicker
  obsL <- melt(obs,id=x) ##convert to stacked data for ggplot
  gjsub <- p1 + geom_point(data=obsL,aes(x=Var1,y=value),color='red') + xlab("Genes sorted by h2") + ylab("h2") + ylim(0,1) + ggtitle(tis %&% ' Global (Joint) Heritability')
  print(gjsub)
}
```


##Local GRM prediction 95% CI comparison
Histograms of the 95% CIs for the local h^2^ estimation in the marginal model (local GRM) and the joint model (local GRM + global GRM) are plotted. 

```{r,message=FALSE,warning=FALSE}
for(i in 1:length(tissues)){
  tis <- tissues[i]
  ##marginal model (local GRM model)
  loconly <- read.table(mydir %&% tis %&% '_h2_localonly_allgenes_100perms_2014-12-19.txt',sep='\t')
  perms <- loconly[,6:105]
  minperms <- apply(perms,1,lci)
  maxperms <- apply(perms,1,uci)
  marginalCI <- maxperms-minperms
  marginalCI[is.na(marginalCI)] <- 0 ##replace NA's with 0
  marginal <- data.frame(marginalCI,"Marginal")
  colnames(marginal) <- c("range","model")
  ##joint model (local + global GRM model)
  locjoint <- read.table(tis %&% '_h2_localjoint_allgenes_100perms_2014-12-19.txt',sep='\t')
  perms <- locjoint[,6:105]
  minperms <- apply(perms,1,lci)
  maxperms <- apply(perms,1,uci)
  jointCI <- maxperms-minperms
  jointCI[is.na(jointCI)] <- 0 ##replace NA's with 0
  joint <- data.frame(jointCI,"Joint")
  colnames(joint) <- c("range","model")
  all <- rbind(marginal,joint)
  p1 <- ggplot(all, aes(x = range, fill = model)) + geom_histogram() + xlab("95% CI (upper - lower)") + ggtitle(tis %&% ' Local GRM h2 estimate 95% CIs')+ facet_grid(model~.)
  print(p1)
  res <- t.test(marginalCI,jointCI) ## is diff b/t joint and marginal CIs significant?
  print(res)
}
```

##95% CIs per gene
Plotted in **black** is the median h^2^ of the 100 permutations, in <span style="color:gray">gray</span> is the 95% CI, and in <span style="color:red">red</span> is the h^2^ from the observed data for the corresponding gene.

###plot all genes
```{r,message=FALSE,warning=FALSE}
for(i in 1:length(tissues)){
  tis <- tissues[i]
  ##local only
  loconly <- read.table(mydir %&% tis %&% '_h2_localonly_allgenes_100perms_2014-12-19.txt',sep='\t')
  obs <- loconly[,5]
  perms <- loconly[,6:105]
  medperms <- apply(perms,1,med)
  seperms <- apply(perms,1,se)
  minperms <- apply(perms,1,lci)
  maxperms <- apply(perms,1,uci)
  
  data <- data.frame(obs,medperms,seperms,minperms,maxperms)
  data <- data %>% arrange(obs) 
  data <- data[complete.cases(data),]
  
  p1 <- ggplot(data,aes(x=1:nrow(data),y=medperms,ymin=minperms, ymax=maxperms) ) + geom_pointrange(col='gray')+geom_point(col='black')+ggtitle(tis %&% ' Local (Only) Heritability')
  losub <- p1 + geom_point(data=data,aes(x=1:nrow(data),y=obs),color='red') + xlab("Genes sorted by observed h2") + ylab("h2") + ylim(0,1)
  print(losub)
  
  ##global only
  gloonly <- read.table(tis %&% '_h2_globalonly_allgenes_100perms_2014-12-19.txt',sep='\t')
  obs <- gloonly[,5]
  perms <- gloonly[,6:105]
  medperms <- apply(perms,1,med)
  seperms <- apply(perms,1,se)
  minperms <- apply(perms,1,lci)
  maxperms <- apply(perms,1,uci)
  
  data <- data.frame(obs,medperms,seperms,minperms,maxperms)
  data <- data %>% arrange(obs) 
  data <- data[complete.cases(data),]
  
  p1 <- ggplot(data,aes(x=1:nrow(data),y=medperms,ymin=minperms, ymax=maxperms) ) + geom_pointrange(col='gray')+geom_point(col='black')+ggtitle(tis %&% ' Global (Only) Heritability')
  gosub <- p1 + geom_point(data=data,aes(x=1:nrow(data),y=obs),color='red') + xlab("Genes sorted by observed h2") + ylab("h2") + ylim(0,1)
  print(gosub)
  
  ##local joint
  locjoint <- read.table(tis %&% '_h2_localjoint_allgenes_100perms_2014-12-19.txt',sep='\t')
  obs <- locjoint[,5]
  perms <- locjoint[,6:105]
  medperms <- apply(perms,1,med)
  seperms <- apply(perms,1,se)
  minperms <- apply(perms,1,lci)
  maxperms <- apply(perms,1,uci)
  
  data <- data.frame(obs,medperms,seperms,minperms,maxperms)
  data <- data %>% arrange(obs) 
  data <- data[complete.cases(data),]
  
  p1 <- ggplot(data,aes(x=1:nrow(data),y=medperms,ymin=minperms, ymax=maxperms) ) + geom_pointrange(col='gray')+geom_point(col='black')+ggtitle(tis %&% ' Local (Joint) Heritability')
  ljsub <- p1 + geom_point(data=data,aes(x=1:nrow(data),y=obs),color='red') + xlab("Genes sorted by observed h2") + ylab("h2") + ylim(0,1)
  print(ljsub)
  
  ##global joint
  glojoint <- read.table(tis %&% '_h2_globaljoint_allgenes_100perms_2014-12-19.txt',sep='\t')
  obs <- glojoint[,5]
  perms <- glojoint[,6:105]
  medperms <- apply(perms,1,med)
  seperms <- apply(perms,1,se)
  minperms <- apply(perms,1,lci)
  maxperms <- apply(perms,1,uci)
  
  data <- data.frame(obs,medperms,seperms,minperms,maxperms)
  data <- data %>% arrange(obs) 
  data <- data[complete.cases(data),]
  
  p1 <- ggplot(data,aes(x=1:nrow(data),y=medperms,ymin=minperms, ymax=maxperms) ) + geom_pointrange(col='gray')+geom_point(col='black')+ggtitle(tis %&% ' Global (Joint) Heritability')
  gjsub <- p1 + geom_point(data=data,aes(x=1:nrow(data),y=obs),color='red') + xlab("Genes sorted by observed h2") + ylab("h2") + ylim(0,1)
  print(gjsub)
}
```

###plot genes w/h^2^ > 0.05
```{r,message=FALSE,warning=FALSE}
for(i in 1:length(tissues)){
  tis <- tissues[i]
  ##local only
  loconly <- read.table(mydir %&% tis %&% '_h2_localonly_allgenes_100perms_2014-12-19.txt',sep='\t')
  obs <- loconly[,5]
  perms <- loconly[,6:105]
  medperms <- apply(perms,1,med)
  seperms <- apply(perms,1,se)
  minperms <- apply(perms,1,lci)
  maxperms <- apply(perms,1,uci)
  
  data <- data.frame(obs,medperms,seperms,minperms,maxperms)
  data <- data %>% arrange(obs) 
  data <- data[complete.cases(data),]
  gt05 <- data[data[,1]>0.05,] ##only genes with obs h2 > 0.05
  
  p1 <- ggplot(gt05,aes(x=1:nrow(gt05),y=medperms,ymin=minperms, ymax=maxperms) ) + geom_pointrange(col='gray')+geom_point(col='black')+ggtitle(tis %&% ' Local (Only) Heritability')
  losub <- p1 + geom_point(data=gt05,aes(x=1:nrow(gt05),y=obs),color='red') + xlab("Genes sorted by observed h2 > 0.05") + ylab("h2") + ylim(0,1)
  print(losub)
  
  ##global only
  gloonly <- read.table(tis %&% '_h2_globalonly_allgenes_100perms_2014-12-19.txt',sep='\t')
  obs <- gloonly[,5]
  perms <- gloonly[,6:105]
  medperms <- apply(perms,1,med)
  seperms <- apply(perms,1,se)
  minperms <- apply(perms,1,lci)
  maxperms <- apply(perms,1,uci)
  
  data <- data.frame(obs,medperms,seperms,minperms,maxperms)
  data <- data %>% arrange(obs) 
  data <- data[complete.cases(data),]
  gt05 <- data[data[,1]>0.05,] ##only genes with obs h2 > 0.05
  
  p1 <- ggplot(gt05,aes(x=1:nrow(gt05),y=medperms,ymin=minperms, ymax=maxperms) ) + geom_pointrange(col='gray')+geom_point(col='black')+ggtitle(tis %&% ' Global (Only) Heritability')
  gosub <- p1 + geom_point(data=gt05,aes(x=1:nrow(gt05),y=obs),color='red') + xlab("Genes sorted by observed h2 > 0.05") + ylab("h2") + ylim(0,1)
  print(gosub)
  
  ##local joint
  locjoint <- read.table(tis %&% '_h2_localjoint_allgenes_100perms_2014-12-19.txt',sep='\t')
  obs <- locjoint[,5]
  perms <- locjoint[,6:105]
  medperms <- apply(perms,1,med)
  seperms <- apply(perms,1,se)
  minperms <- apply(perms,1,lci)
  maxperms <- apply(perms,1,uci)
  
  data <- data.frame(obs,medperms,seperms,minperms,maxperms)
  data <- data %>% arrange(obs) 
  data <- data[complete.cases(data),]
  gt05 <- data[data[,1]>0.05,] ##only genes with obs h2 > 0.05
  
  p1 <- ggplot(gt05,aes(x=1:nrow(gt05),y=medperms,ymin=minperms, ymax=maxperms) ) + geom_pointrange(col='gray')+geom_point(col='black')+ggtitle(tis %&% ' Local (Joint) Heritability')
  ljsub <- p1 + geom_point(data=gt05,aes(x=1:nrow(gt05),y=obs),color='red') + xlab("Genes sorted by observed h2 > 0.05") + ylab("h2") + ylim(0,1)
  print(ljsub)
  
  ##global joint
  glojoint <- read.table(tis %&% '_h2_globaljoint_allgenes_100perms_2014-12-19.txt',sep='\t')
  obs <- glojoint[,5]
  perms <- glojoint[,6:105]
  medperms <- apply(perms,1,med)
  seperms <- apply(perms,1,se)
  minperms <- apply(perms,1,lci)
  maxperms <- apply(perms,1,uci)
  
  data <- data.frame(obs,medperms,seperms,minperms,maxperms)
  data <- data %>% arrange(obs) 
  data <- data[complete.cases(data),]
  gt05 <- data[data[,1]>0.05,] ##only genes with obs h2 > 0.05
  
  p1 <- ggplot(gt05,aes(x=1:nrow(gt05),y=medperms,ymin=minperms, ymax=maxperms) ) + geom_pointrange(col='gray')+geom_point(col='black')+ggtitle(tis %&% ' Global (Joint) Heritability')
  gjsub <- p1 + geom_point(data=gt05,aes(x=1:nrow(gt05),y=obs),color='red') + xlab("Genes sorted by observed h2 > 0.05") + ylab("h2") + ylim(0,1)
  print(gjsub)
}
```