---
title: "Analyze Cis/Trans Heritability"
author: "Hae Kyung Im"
date: "November 30, 2014"
output: html_document
---

```{r, echo=FALSE}

rm(list=ls())
options(digits=3,digits.sec=4,max.print=200)
## other options (width=120,error=recover,,device="quartz")
## options(warn=2) ## converts warnings into errors

## useful libraries

library(qvalue)
library(MASS)
library(reshape)
library(Hmisc)
library(dplyr)
library(ggplot2)

## paste operator

"%&%" <- function(a, b) paste(a, b, sep="")

## this file has functions that I use most often

pre0 <- '/Users/haky/Work/im-lab/'

source(pre0 %&% 'nas40t2/haky/R_functions/myfunctions2.r')
source(pre0 %&% 'nas40t2/haky/R_functions/mygenetic.r')

## define subdirectories

pre <- '/Users/haky/GitHub/cross-tissue/analysis/'
input_dir <- pre %&% 'input/'
output_dir <- pre %&% 'output/'
plot_dir <- pre %&% 'plots/'
tempo_dir <- pre %&% 'tempo/'
source_dir <- pre %&% "sources/"
work_dir <- pre

## functions specific to the project
##source(source.dir %&% "functions.r")

## working directory

setwd(work_dir)

## read the data

##data <- read.table(file=input.dir %&% "data.txt",sep='\t', header=T, as.is=T)


```


```{r}

h2_global <- read.table(input_dir %&% 'DGN-WB.globalGRM.h2.exp.2014-08-27.txt',header=T,as.is=T)
h2_local <- read.table(input_dir %&% 'DGN-WB.localGRM.h2.exp.2014-08-30.txt',header=T,as.is=T)
h2_both <- read.table(input_dir %&% 'DGN-WB.localGRM.plus.globalGRM.h2.exp.2014-09-05.txt',header=T,as.is=T)

h2alkes <- read.table(input_dir %&% 'alkes-h2all.txt',header=T,as.is=T)
h2fred <- read.table(input_dir %&% 'fred-h2PB.txt',header=T,as.is=T)
names(h2alkes)[names(h2alkes)=='gname'] = 'gene'
names(h2fred)[names(h2fred)=='gname'] = 'gene'

str(h2_global)
str(h2_local)
str(h2_both)
```
TODO: Why only 13648 genes in h2 local. Did GCTA not converge? Investigate why.

```{r}
names(h2_global) = c("gene", "global0.h2",   "global0.se",   "global0.p"  )
names(h2_local) = c("gene", "local0.h2",   "local0.se",   "local0.p"  )
## join heritability estimates
h2all = inner_join(h2_global,h2_local,by=c('gene'))
h2all = inner_join(h2all,h2_both,by=c('gene'))

h2all2 = inner_join(h2all,h2alkes,by=c('gene'))
h2all2 = inner_join(h2all2,h2fred,by=c('gene'))

## sort by h2 and plot
## - [ ] h2 global0
## - [ ] h2 local0
## - [ ] h2 global
## - [ ] h2 local

# plot global0
data <- h2all %>% select(global0.h2,global0.se) %>% arrange(global0.h2) 
names(data) = c('h2','se')
data <- data %>% mutate(ymin = pmax(0, h2 - 2 * se), ymax = pmin(1, h2 + 2 * se) )
ggplot(data,aes(x=1:nrow(data),y=h2,ymin=ymin, ymax=ymax) ) + geom_pointrange(col='gray')+geom_point()+ggtitle('global (only) Heritability')

##ggplot(data,aes(x=1:nrow(data),y=h2,ymin=ymin,ymax=ymax) ) + geom_point() + geom_point(aes(y=ymin),col='gray')+ geom_point(aes(y=ymax),col='gray')


# plot local0
data <-  h2all %>% select(local0.h2,local0.se) %>% arrange(local0.h2)
names(data) = c('h2','se')
data <- data %>% mutate(ymin = pmax(0, h2 - 2 * se), ymax = pmin(1, h2 + 2 * se) )
ggplot(data,aes(x=1:nrow(data),y=h2,ymin=ymin, ymax=ymax) ) + geom_pointrange(col='gray')+geom_point()+ggtitle('Local (only) Heritability')

# plot local (estimated jointly with global)
data <-  h2all %>% select(local.h2,local.se) %>% arrange(local.h2)
names(data) <- c('h2','se')
data <- data %>% mutate(ymin = pmax(0, h2 - 2 * se), ymax = pmin(1, h2 + 2 * se) )
ggplot(data,aes(x=1:nrow(data),y=h2,ymin=ymin, ymax=ymax) ) + geom_pointrange(col='gray')+geom_point()+ggtitle('Local (joint) Heritability')

# plot global (estimated jointly with local)
data <-  h2all %>% select(global.h2,global.se) %>% arrange(global.h2)
names(data) <- c('h2','se')
data <- data %>% mutate(ymin = pmax(0, h2 - 2 * se), ymax = pmin(1, h2 + 2 * se) )
ggplot(data,aes(x=1:nrow(data),y=h2,ymin=ymin, ymax=ymax) ) + geom_pointrange(col='gray')+geom_point()+ggtitle('Global (joint) Heritability')


global.ind <- with(h2all, global.h2 - global.se * 2 > 0)
global0.ind <- with(h2all, global0.h2 - global0.se * 2 > 0)
local.ind <- with(h2all, local.h2-local.se * 2 > 0)
local0.ind <- with(h2all, local0.h2-local0.se * 2 > 0)

## - [ ] look at genes that didnt converge for local grm

```

TODO: how do Alkes and Fred estimate negative heritability?
Alkes allows negative h2 but total variance is still positive definite because `h2*GRM + (1-h2)*I`, but interpretation is all messed up. Variance component `h2*GRM` cannot be negative definite.

Results below show that if we only look at positive h2 estimates, the correlation between Alkes' heritability and Heathers becomes slightly larger.

```{r}

h2all2 %>% filter(h2bloodcis>0) %>% with(cor.test(h2bloodcis,local.h2,method='spearman'))
```
vs.
```{r}
h2all2  %>% with(cor.test(h2bloodcis,local.h2,method='spearman'))

h2all2 %>% filter(h2bloodtra>0) %>% with(cor.test(h2bloodtra,global.h2,method='spearman'))

```
vs.
```{r}
h2all2  %>% with(cor.test(h2bloodtra,global.h2,method='spearman'))

```

TODO:
compare adipose-specific h2 to alkes-adipose h2
alkes-adipose ~ adipose-specific + cross tissue
alkes-blood ~ blood-specific + cross tissue

alkes-adipose ~ other-tissue-specific + cross tissue
